Democratizing MPC

### 2017-10-03 OaklandSubmission/eval.tex
minor

We first implement benchmarks of ~\cite{shafindss} and~\cite{minionn} in \tool.
Next, we show the generality of \tool by implementing state-of-the-art machine learning models
. 
lin
nb
tree\\
minion-cnn
secureml
cryptonet\\
logistic
cnn
bonsai\\
cifar

>>>>

\section{Evaluation}
\label{sec:eval}

We first implement benchmarks of ~\cite{shafindss} and~\cite{minionn} in \tool.
Next, we show the generality of \tool by implementing state-of-the-art machine learning models.
Finally, we discuss a model that requires pipelinig.
Our results are in two settings, a LAN setting and a cross-continent WAN setting.
The round trip time for two machines in a LAN setting is 1ms and in WAN setting is 40ms.

\subsection{Standard models}
\label{sec:shallow}
We consider three types of classifiers: linear, Naive Bayes, and decision trees. 
These classifiers are trained on the followinng data sets from the UCI  machine learning repository:
 the Wisconsin Breast Cancer data set, 
Credit Approval data set, Audiology (Standardized) data set, Nursery data set, and
ECG (electrocardiogram) classification data from~\cite{barni}.

%dataset  | size | gates | and | mul | depth

%dataset | time | comm | timeL | commL | timeW | commW

lin
nb
tree\\
minion-cnn
secureml
cryptonet\\
logistic
cnn
bonsai\\
cifar
